Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Updated Question Mark
Updated Scripts

@@

The proposed survey is designed using Google Forms,
https://docs.google.com/forms/d/e/1FAIpQLSeHHeKaryNQ6sKgbuOH-ZgXwQYkNw9jBdxIbgeXWVj_t1ob2w/viewform?usp=sf_link

@@

7. **In which U.S. state do you currently reside**
  - ______________

>>>>

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
all_states <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", "Missouri", "Montana", "Nebraska", "Nevada", "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", "Tennessee", "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming")

just_harris <- read.csv(here("data/02-analysis_data/just_harris.csv"))
just_harris$end_date <- as.Date(just_harris$end_date)
just_harris$predicted_pct <- predict(linear_model, newdata = just_harris)

# Calculate the average pct for each state
state_avg_pct <- just_harris %>%
  group_by(state) %>%
  summarize(avg_pct = mean(pct, na.rm = TRUE))

# Classify each state as a "win" or "loss" based on a 50% threshold and handle NA values
state_avg_pct <- state_avg_pct %>%
  mutate(win_state = ifelse(avg_pct > 50, "Harris Win", "Harris Loss"))

# Replace NA values with "Uncertain"
state_avg_pct$win_state[is.na(state_avg_pct$win_state)] <- "Uncertain"

# Convert win_state to a factor to control levels and ensure "Uncertain" is displayed in the legend
state_avg_pct$win_state <- factor(state_avg_pct$win_state, levels = c("Harris Win", "Harris Loss", "Uncertain"))
existing_states <- unique(state_avg_pct$state)
missing_states <- setdiff(all_states, existing_states)
missing_states_df <- data.frame(
  state = missing_states,
  avg_pct = NA,  # No average percentage available
  win_state = "Uncertain"
)
state_avg_pct_complete <- bind_rows(state_avg_pct, missing_states_df)
state_avg_pct_complete <- state_avg_pct_complete %>% arrange(state)

state_avg_pct_complete$win_state <- factor(state_avg_pct_complete$win_state, 
                                           levels = c("Harris Win", "Harris Loss", "Uncertain"))

# Plot the map with the updated classifications
plot_usmap(data = state_avg_pct_complete, values = "win_state", regions = "states") +
  scale_fill_manual(values = c("Harris Win" = "blue", "Harris Loss" = "red", "Uncertain" = "gray"), 
                    name = "Prediction Outcome") +
  labs(title = "Predicted 2024 Presidential Election Outcome for Kamala Harris",
       subtitle = "States where Kamala Harris is predicted to win (blue) or lose (red), unpolled states as Uncertain (gray)") +
  theme_minimal()

```

@@

The proposed survey is designed using Google Forms,
https://forms.gle/Vhmm1b1XnqTSoBWq8

@@

7. **In which U.S. state do you currently reside?**
  - ___
